---
title: "Descriptive Results"
output: html_notebook
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Items:

-` MP`  
  If there is a black square then there is a yellow circle.  
  There is a black square.  
  Conclusion: There is a yellow circle.  
- `AC`  
  If there is a yellow circle then there is a black square.  
  There is a black square.  
  Conclusion: There is a yellow circle.  
- `MPF`  
  If there is a black square then there is a yellow circle.  
  There is NOT a black square.  
  Conclusion: There is a yellow circle.  
- `ACF`  
  If there is a yellow circle then there is a black square.  
  There is NOT a black square.  
  Conclusion: There is a yellow circle.  
- `CB`  
  There is a black square and there is a yellow circle. / There is a yellow circle and there is a black square.  
  There is a black square.  
  Conclusion: There is a yellow circle.  
- `DB`  
  There is a black square or there is a yellow circle. / There is a yellow circle or there is a black square.  
  There is a black square.  
  Conclusion: There is a yellow circle.  
- `CF`  
  There is a black square and there is a yellow circle. / There is a yellow circle and there is a black square.  
  There is NOT a black square.  
  Conclusion: There is a yellow circle.  
- `DF`  
  There is a black square or there is a yellow circle. / There is a yellow circle or there is a black square.  
  There is NOT a black square.  
  Conclusion: There is a yellow circle.


```{r, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#load the appropriate packages
library(afex)
lsm.options(lmer.df = "asymptotic")
library (readr)
library (ggplot2)
require(latticeExtra)
lattice.options(default.theme = standard.theme(color = FALSE))
lattice.options(default.args = list(as.table = TRUE))
require(dplyr)
require(tidyr)

add_conditions <- function(data) {
  data$CondType <- factor(data$CondType, levels = c("MP", "AC", "MPF", "ACF", "CB", "DB", "CF", "DF"))
  data$inference <- car::recode(data$CondType, 
                                "c('MP', 'MPF')='MP';
                                 c('AC', 'ACF')='AC';
                                 c('CB', 'CF')='conj';
                                 c('DB', 'DF')='disj'", 
                                levels = c("MP", "AC", "conj", "disj"))
  data$polarity_premise <- car::recode(data$CondType, 
                                       "c('MP', 'AC', 'CB', 'DB')='positive'; 
                                        c('MPF', 'ACF', 'CF', 'DF')='negative'", 
                                       levels = c("positive", "negative"))
  data$validity <- factor(ifelse(data$CondType %in% c("MP", "CB", "DF"), "valid", 
                                 ifelse(data$CondType %in% c("AC", "ACF", "DB", "CF"), "possible", 
                                        "impossible")), 
                          levels = c("valid", "possible", "impossible"))
  data$quasi_validity <- car::recode(data$CondType, 
                                      "c('MP', 'AC', 'CB', 'DF')='quasi_valid'; 
                                      c('MPF', 'ACF', 'CF', 'DB')='quasi_invalid'", 
                                      levels = c("quasi_valid", "quasi_invalid"))
  data$major_premise <- factor(ifelse(data$CondType %in% c("MP", "AC", "MPF", "ACF"), "conditional", "conjunction-disjunction"), levels = c( "conditional", "conjunction-disjunction"))
  data
}

```


# First Pass

```{r, results='hide'}
d_fp <- read_csv("FP.csv")
d_fp <- add_conditions(d_fp)
attr(d_fp, "spec") <- NULL
str(d_fp)

d_fp_a <- d_fp %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(CondType, dv) %>% 
  summarise(mean_fp = mean(rt, na.rm = TRUE))

d_fp_a2 <- d_fp %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(inference, polarity_premise, dv) %>% 
  summarise(mean_fp = mean(rt, na.rm = TRUE))
```


Mean first pass RTs as a function of condition:

```{r, fig.width=10, fig.height=4}
xyplot(mean_fp ~ CondType|dv, d_fp_a, type = "o")
```

Mean first pass RTs as a function of `inference` and `polarity`:

```{r, fig.width=10, fig.height=4}
xyplot(mean_fp ~ inference|dv, d_fp_a2, group = polarity_premise, type = "o", auto.key = list(lines=TRUE))
```


# Total Time

```{r, results='hide'}
d_tt <- read_csv("TT.csv")
d_tt <- add_conditions(d_tt)
attr(d_tt, "spec") <- NULL
str(d_tt)

d_tt_a <- d_tt %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(CondType, dv) %>% 
  summarise(mean_tt = mean(rt, na.rm = TRUE))

d_tt_a2 <- d_tt %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(inference, polarity_premise, dv) %>% 
  summarise(mean_tt = mean(rt, na.rm = TRUE))
```


Mean total RTs as a function of condition:

```{r, fig.width=10, fig.height=4}
xyplot(mean_tt ~ CondType|dv, d_tt_a, type = "o")
```

Mean total RTs as a function of `inference` and `polarity`:

```{r, fig.width=10, fig.height=4}
xyplot(mean_tt ~ inference|dv, d_tt_a2, group = polarity_premise, type = "o", auto.key = list(lines=TRUE))
```


# Regression (RI)

```{r, results='hide'}
d_ri <- read_csv("RI.csv")
d_ri <- add_conditions(d_ri)
attr(d_ri, "spec") <- NULL
str(d_ri)

d_ri_a <- d_ri %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(CondType, dv) %>% 
  summarise(mean_ri = mean(rt, na.rm = TRUE))

d_ri_a2 <- d_ri %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(inference, polarity_premise, dv) %>% 
  summarise(mean_ri = mean(rt, na.rm = TRUE))
```


Mean rate of RI as a function of condition:

```{r, fig.width=10, fig.height=4}
xyplot(mean_ri ~ CondType|dv, d_ri_a, type = "o")
```

Mean rate of RI as a function of `inference` and `polarity`:

```{r, fig.width=10, fig.height=4}
xyplot(mean_ri ~ inference|dv, d_ri_a2, group = polarity_premise, type = "o", auto.key = list(lines=TRUE))
```


# Regression Path 

```{r, results='hide'}
d_rp <- read_csv("RP.csv")
d_rp <- add_conditions(d_rp)
attr(d_rp, "spec") <- NULL
str(d_rp)

d_rp_a <- d_rp %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(CondType, dv) %>% 
  summarise(mean_rp = mean(rt, na.rm = TRUE))

d_rp_a2 <- d_rp %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(inference, polarity_premise, dv) %>% 
  summarise(mean_rp = mean(rt, na.rm = TRUE))
```


Mean RP as a function of condition:

```{r, fig.width=10, fig.height=4}
xyplot(mean_rp ~ CondType|dv, d_rp_a, type = "o")
```

Mean RP as a function of `inference` and `polarity`:

```{r, fig.width=10, fig.height=4}
xyplot(mean_rp ~ inference|dv, d_rp_a2, group = polarity_premise, type = "o", auto.key = list(lines=TRUE))
```



# Regression (RO)

```{r, results='hide'}
d_ro <- read_csv("RO.csv")
d_ro <- add_conditions(d_ro)
attr(d_ro, "spec") <- NULL
str(d_ro)

d_ro_a <- d_ro %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(CondType, dv) %>% 
  summarise(mean_ro = mean(rt, na.rm = TRUE))

d_ro_a2 <- d_ro %>% 
  gather("dv", "rt", Antecedent:Conclusion) %>% 
  group_by(inference, polarity_premise, dv) %>% 
  summarise(mean_ro = mean(rt, na.rm = TRUE))
```


Mean rate of RO as a function of condition:

```{r, fig.width=10, fig.height=4}
xyplot(mean_ro ~ CondType|dv, d_ro_a, type = "o")
```

Mean rate of RO as a function of `inference` and `polarity`:

```{r, fig.width=10, fig.height=4}
xyplot(mean_ro ~ inference|dv, d_ro_a2, group = polarity_premise, type = "o", auto.key = list(lines=TRUE))
```


